TBD

### 2024-04-02 outputs/paper/paper.qmd
paper updated

---
title: ""
subtitle: ""
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/House_Price.git"
date: today
date-format: long
abstract: ""
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

@@

# read in data
file_path_0 <- "../../inputs/data/cali_house_price.csv"
file_path_1 <- "../../outputs/data/cali_house_price_clean.csv"
file_path_2 <- "../../outputs/data/.csv"
file_path_3 <- "../../outputs/data/.csv"

cali_house_price <- read_csv(file_path_0, show_col_types = FALSE)
cali_house_price_clean<- read_csv(file_path_1, show_col_types = FALSE)

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: fig-trends-1
#| fig-cap: Trend for Alberta Mortality-Top 5 Causes

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: fig-trends-2
#| fig-cap: Trend for Alberta Mortality-Sum of Causes

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-summary
#| tbl-cap: summary of modeling

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: fig-models
#| fig-cap: Model Results
#| fig-subcap: ["Poisson Model","Negative Binomial Model"]
#| layout-ncol: 2
#| layout-nrow: 1

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-cross_validation
#| tbl-cap: cross validation of modeling

>>>>

---
title: "TBD"
subtitle: "TBD"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/House_Price.git"
date: today
date-format: long
abstract: "TBD"
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

@@

# read in data
file_path_0 <- "../../inputs/data/cali_house_price.csv"
file_path_1 <- "../../outputs/data/cali_house_price_clean.csv"
file_path_2 <- "../../outputs/data/ocean_proximity_frequency.csv"
file_path_3 <- "../../outputs/data/.csv"

cali_house_price <- read_csv(file_path_0, show_col_types = FALSE)
cali_house_price_clean<- read_csv(file_path_1, show_col_types = FALSE)
ocean_proximity_frequency<- read_csv(file_path_2, show_col_types = FALSE)

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: fig-ocean_proximity_frequency
#| fig-cap: Frequency of Ocean Proximity

ggplot(ocean_proximity_frequency, aes(x = Variable, y = Frequency)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(title = "Frequency of Categories in Ocean Proximity",
       x = "Ocean Proximity",
       y = "Frequency") +
  coord_flip()

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: fig-TBD_1
#| fig-cap: TBD

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-TBD_2
#| tbl-cap: TBD

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: fig-TBD_3
#| fig-cap: TBD

@@

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-pos: 'h'
#| label: tbl-TBD_4
#| tbl-cap: TBD
